\emeszida

### 2024-03-29 sigbovik/paper.tex
Cuneiform abstract

\setmainfont[Ligatures=TeX]{Times New Roman}
\newfontfamily\arabicfont
    [Script=Arabic,     % to get correct arabic shaping
    Scale=1.2]          % make the arabic font bigger, a matter of taste
        {Arial}     % whatever Arabic font you like

@@

\begin{abstract}[\cuneiform{𒉆𒆸}]
test
\end{abstract}

@@

\section{Description of the Texts}
The tablets preserve a number of methods for performing simple neural network calculations.
Simple array operations as well as the calculation of the dot product are included in the corpus.
All of this comes together in the large perceptron tablet.
It is clear that the cuneogrammers were slowly developing their skills as some of the earlier and simpler methods date as far back as the Old Akkadian period (c. 2300--2150 BCE) while the perceptron tablet is from the Old Babylonian period (c. 1900--1600 BCE).
The longest tablet, included in the appendix, \hl{shows a fully featured perceptron ADD MORE HERE}
Interestingly, the long weights at the end of the tablet very closely resemble the parameters of later astronomical calculations (see Figure \ref{fig:BM_34580}).

\hl{- add graph plotting perceptron output vs true trigonometric ratios from Plimpton}

>>>>

% \setmainfont[Ligatures=TeX]{Times New Roman}
\newfontfamily\arabicfont
    [Script=Arabic,     % to get correct arabic shaping
    Scale=1.2]          % make the arabic font bigger, a matter of taste
        {Arial}     % whatever Arabic font you like

@@

\begin{abstract}[\cuneiform{𒉆𒆸}]
\cuneiform{𒀭𒉏𒁾𒅅𒉈𒈠𒌝𒈠𒊺𒀪𒃻𒌺𒃌𒀀𒁲}
\cuneiform{𒐉𒅆𒅆𒌓𒂊𒁹𒅆𒁾𒎌𒃻𒉆𒅆𒌇𒀭𒉏𒉆}
\cuneiform{𒅆𒀸𒁾𒉿𒇷𒅎𒆗𒐊𒎙𒈫𒆕𒁾𒉿𒇷𒅎}
\cuneiform{𒆗𒐊𒎙𒈫𒈤𒃲𒀸𒄒𒋥𒇹𒋾𒅴𒋃𒀀𒊭𒆳}
\cuneiform{𒅴𒂠𒅇𒌵𒆠𒅴𒋃𒀀𒁾𒊬𒆕𒎌𒀭𒉏}
\cuneiform{𒅴𒋗𒅆𒌑𒋃𒎌𒌇𒊭𒄑𒁍}
\end{abstract}

@@

\section{Description of the Texts}
The Sealand corpus contains numerous fragments implementing recognizable procedures such as bit-shifting, populating an array, computing dot products, and so on. 
However, only a single text is known to have been preserved in its entirety.\footnote{All of the known texts are reproduced in \url{github.com/MrLogarithm/emeszida/tree/main/programs}}
Spanning close to 1700 lines, this impressive text is divided into five sections implementing what modern readers will immediately recognize to be a multi-layer perception.
The first section straightforwadly defines a matrix-multiplication subroutine. 
This is called by a subroutine defined in section two, which applies each layer of the perceptron to a given input, and applies a ReLU-style activation between each pair of layers.
Section three implements the tablet's ``main'' method, which loads an input to memory, calls the perceptron subroutine, and prints the resulting output.
Section four loads the model parameters, which appear to comprise weight matrices of sizes $50\times 2$, $25\times 50$, and $1\times 25$, plus bias vectors of sizes $50$, $25$, and $1$ respectively.
The final section lists pairs of inputs, whose values (incredibly!) correspond to the second and third columns of Plimpton 322.

When the program is executed, it produces a single numeric output for each input pair. 
These outputs correspond remarkably closely to the values in the first column of Plimpton 322, as demonstrated in Figure~\ref{fig:graph}.
The correspondence is not perfect, however, and the values which should match lines 1, 5, and 6 of Plimpton 322 are significantly larger than expected.
This implies that, although the code on this tablet is clearly \textit{related} to Plimpton 322, it could not have been used to directly populate the table in that text.
Perhaps the outputs from this model were refined in some later step to produce the more exact ratios in the Plimpton text, or perhaps the Babylonians were disillusioned by the imprecision of their machine learning models and simply abandoned them for tried-and-true manual methods. 
Given how miniscule the cuneigramming corpus is relative to the larger body of Babylonian administrative writing, we lean towards the latter explanation.

\begin{figure}\label{fig:graph}
    \includegraphics[width=0.5\textwidth]{graph.png}
    \caption{Outputs from the perceptron tablet vs.\ true value of each line from column 1 of Plimpton 322. If a points falls upon the line, the model output for that line exactly equals the value on Plimpton 322.}
\end{figure}

The tablets preserve a number of methods for performing simple neural network calculations.
Simple array operations as well as the calculation of the dot product are included in the corpus.
All of this comes together in the large perceptron tablet.
It is clear that the cuneogrammers were slowly developing their skills as some of the earlier and simpler methods date as far back as the Old Akkadian period (c. 2300--2150 BCE) while the perceptron tablet is from the Old Babylonian period (c. 1900--1600 BCE).
The longest tablet, included in the appendix, \hl{shows a fully featured perceptron ADD MORE HERE}
Interestingly, the long weights at the end of the tablet very closely resemble the parameters of later astronomical calculations (see Figure \ref{fig:BM_34580}).
